---
title: "EDA of Animes by Studio SHAFT"
output: 
  html_notebook:
      code_folding: hide
      toc: true
      toc_float: true
---

```{r include = FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

## Load Libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Import and View Data
```{r message = FALSE}
df <- readr::read_csv("data/processed_data.csv")

# grouping rare sources into 'other'
df <- mutate(df,
    Src = if_else(Src %in% c("Music", "-"),
                  "Other",
                  if_else(Src == "Novel", "Light novel", Src)
    )
  ) 
# set theme
theme_set(theme_light())

head(df, 10)
```

## Univariate Analysis
### Episodes
summary statistics:
```{r}
summary(df$Eps)

df %>%
  ggplot(aes(x = Eps)) +
  geom_histogram(binwidth = 6.5) +
  labs(
    title = "Distribution of Number of Episodes",
    x = "Number of Episodes",
    y = "Count"
  )
```

### Members
summary statistics:
```{r}
summary(df$Members)

df %>%
  ggplot(aes(x = Members)) +
  geom_histogram(binwidth = 106700) +
  labs(
    title = "Distribution of Number of Members",
    x = "Members",
    y = "Count"
  )
df %>%
  ggplot(aes(x = Members)) +
  geom_histogram() +
  scale_x_log10(labels = scales::comma) +
  labs(
    title = "Distribution of Number of Members on Log Scale",
    x = "Members",
    y = "Count"
  )
```

### Score
summary statistics:
```{r}
summary(df$Score)

df %>%
  ggplot(aes(x = Score)) +
  geom_histogram(binwidth = 0.6) +
  labs(
    title = "Distribution of Scores",
    x = "Scores",
    y = "Count"
  )
```

### Sources
```{r}
df %>%
  count(Src) %>%
  ggplot(aes(x = reorder(Src, n), y = n)) +
  geom_bar(stat = "identity", width = 0.6) +
  labs(
   title = "Comparison of Different Anime Sources",
   x = "Source",
   y = "Count"
  )
```

### Genres
```{r}
# new df in long format
categorical <- df %>%
  separate(Genres, paste("G", 1:9), sep = ",", extra = "drop") %>%
  pivot_longer(c(4:12), values_to = "Genre", values_drop_na = TRUE) %>%
  select(-name)

categorical %>%
  count(Genre) %>%
  ggplot(aes(x = reorder(Genre, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(
    title = "Comparison of Genres",
    x = "Genre",
    y = "Count"
  )

# top 10 genres
top10 <- categorical %>%
  count(Genre) %>%
  top_n(10)

top10 %>%
  ggplot(aes(x = reorder(Genre, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(
    title = "Top 10 Genres",
    x = "Genre",
    y = "Count"
  )
```

## Bivariate Analysis
### Eps and Score
```{r}
df %>%
  ggplot(aes(x = Eps, y = Score, na.rm = TRUE)) +
  geom_point() +
  ggtitle("Score by Number of Episodes")
```

#### Correlation Test
```{r}
cor.test(df$Score, df$Eps, method = "pearson")
```

### Members and Score
```{r}
lin <- df %>%
  ggplot(aes(x = Members , y = Score)) +
  geom_point() +
  ggtitle("Score by Number of Members") 

# in log scale
log <- df %>%
  ggplot(aes(x = Members , y = Score)) +
  geom_point() +
  scale_x_log10(labels = scales::comma) +
  ggtitle("Score by Number of Members in Log Scale") 

gridExtra::grid.arrange(lin, log)
```

#### Correlation Test
```{r}
cor.test(df$Score, df$Members, method = "pearson")
```

### Members and Eps
```{r}
df %>%
  ggplot(aes(x = Members, y = Eps)) +
  geom_point() +
  ggtitle("Number of Epidodes by Number of Members")
```

#### Correlation Test
```{r}
cor.test(df$Eps, df$Members, method = "pearson")
```

### Score and Source
```{r}
df %>%
  mutate(Src = as.factor(Src)) %>%
  group_by(Src) %>%
  ggplot(aes(x = Src, y = Score)) +
  geom_boxplot() +
  labs(
    title = "Distribution of Score Grouped by Source",
    x = "Source"
  )
```

### Score and Genre
```{r}
categorical %>%
  filter(Genre %in% top10$Genre) %>%
  ggplot(aes(x = Genre, y = Score)) +
  geom_boxplot() +
  coord_flip() +
  labs(
    title = "Distribution of Score of Top 10 Genres",
    x = "Genre",
    y = "Score"
  )

